## Spatial weight matrix


```{r}
library(tidyverse)
library(spdep)
```

- Read the dataset.
```{r, echo=TRUE}
d <- read_csv("./data/trait_env.csv")
d
```

```{r, echo=TRUE}
(nb <- cell2nb(length(unique(d$x)),length(unique(d$y)), type = "queen"))
```

```{r, echo=TRUE}
(W <- nb2listw(nb, zero.policy = TRUE, style = "W"))
```

## Fit

- Intercept only
```{r, echo=TRUE}
fit1 <- spautolm(trait ~ 1, listw = W, data = d)

summary(fit1)
```

- lambda (rho) = `r fit1$lambda` indicates a positve spatial autocorrelaiton



- Model with an environmetal predictor
```{r, echo=TRUE}
fit2 <- spautolm(trait ~ hab, listw = W, data = d)

summary(fit2)
```
- lambda (rho) = `r fit2$lambda` indicates a weak positve spatial autocorrelaiton
- Negative `habvalley` indicates valley sites have negative effects on trait values compared to ridge sites even after controlling spatial autocorrelaiton.

## Exercise 

```{r, echo=TRUE, eval=TRUE}
d2 <- d %>%
  mutate(pred1 = fit1$fit$fitted.values) %>%
  mutate(res1 = fit1$fit$residuals) %>%
  mutate(pred2 = fit2$fit$fitted.values) %>%
  mutate(res2 = fit2$fit$residuals) 

ggplot(d2, aes(x = x, y = y, fill = pred1)) +
    geom_raster()
```

- Predicitons (expected trait means) that account for the spatial autocorrleation.
- The pattern is smoother than the observation.
```{r, echo=TRUE, eval=TRUE}
ggplot(d2, aes(x = x, y = y, fill = res1)) +
    geom_raster()
```

- Residuals (trait deviation from plot means) that were not explained by the spatial autocorrleation.
```{r, echo=FALSE, eval=FALSE}
ggplot(d2, aes(x = x, y = y, fill = pred2)) +
    geom_raster()
```
```{r, echo=FALSE, eval=FALSE}
ggplot(d2, aes(x = x, y = y, fill = res2)) +
    geom_raster()
```

```{r, echo=TRUE, eval=TRUE}
d2 %>%
  ggplot(., aes(x = hab, y = pred1, col = hab)) +
  geom_violin() +
  geom_jitter(width = 0.2)
```

- Ridge sites have grater trait values 
```{r, echo=TRUE, eval=TRUE}
d2 %>%
  ggplot(., aes(x = hab, y = res1, col = hab)) +
  geom_violin() +
  geom_jitter(width = 0.2)
```

- Ridge sites have greater trait values after removing the spatial autocorrleation.